Multiphyscis modeling for the Fluoride-salt-cooled High-temperature Reactor (FHR)

### 2018-07-22 paper/main.tex
Updates from ShareLaTeX

The time constant of the system is compared via zero power reactivity insertion transient simulations. External reactivity is inserted into the core at norminal zero power conditions and without temperature reactivity feedback that would stablize the power at a certain level, the reactor power increases exponentially due to excess external reactivity, as shown in equation \ref{eq:pexp}. 
The speed in which the power ramps up is a direct characteristic of the reactor time scale in the model, as shown in equation \ref{eq:pexp}.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\columnwidth]{./images/benchmark/fuel_feedback.png}
  \includegraphics[width=0.6\columnwidth]{./images/benchmark/flibe_feedback.png}
  \caption{Comparison between the diffusion based model and the Monte Carlo based model for fuel and flibe temperature (and void) feedback effect. Error bar shows statistical error in Monte Carlo results.} 
  \label{fig:fuel_feedback}
\end{figure}

% \begin{figure}[h]
%   \centering
%   \includegraphics[width=0.6\columnwidth]{./images/benchmark/flibe_feedback.png}
%   \caption{Comparison between the diffusion based model and the Monte Carlo based model for flibe temperature feedback effect. Error bar shows statistical error in Monte Carlo results.} 
%   \label{fig:flibe_feedback}
% \end{figure}

@@

\subsection{Steady state results}
After careful code-to-code verification for the multi-physics model, parameters such as power, flibe and fuel temperatures, and neutron flux are computed with design parameters in Table \ref{tab:tmsr_design}. Uniform temperature and uniform upward velocity are imposed as the inlet boundary condition. Vacuum boundary condition for neutron diffusion is used outside of the reflector.

% flux
An eight-group energy structure is used in the neutron diffusion equations but the neutron flux values are regrouped into thermal ([0.00E+00, 5.00E-07] MeV) and fast ([5.00E-07, 1.40E+00] MeV) regions for plotting purpose. As confirmed by the plots, fast neutrons are generated exclusively from nuclear reactions in the fuel region and are then scattered by the matters in the core as they get thermalized. 
The moderation effect of the coolant is dwarfed by that of the graphite reflector in TMSR. As a result, a large portion of thermal neutrons is found inside the reflector, besides the center of the core.

The thermal neutrons that travel back from the reflector to the fuel region cause a peak in power density near the border as they trigger nuclear reactions. 
% power
As shown in figure \ref{fig:tmsr_power_ss}, the power peaks at the center of the fuel region, decreases outward and increases again next to the reflector boundaries due to the moderation effect of the graphite reflector. This confirms that the neutron diffusion based model captures the boundary effect adequately. The radial power peaking in TMSR SF-1 is 1.24 at nominal conditions with fresh fuel.

@@

>>>>

The time constant of the system is compared via zero power reactivity insertion transient simulations. External reactivity is inserted into the core at norminal zero power conditions and without temperature reactivity feedback that would stablize the power at a certain level, the reactor power increases exponentially due to excess external reactivity, as shown in Equation \ref{eq:pexp}. 
The speed in which the power ramps up is a direct characteristic of the reactor time scale in the model, as shown in equation \ref{eq:pexp}.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\columnwidth]{./images/benchmark/feedback_fuel.png}
  \includegraphics[width=0.6\columnwidth]{./images/benchmark/feedback_flibe.png}
  \caption{Comparison between the diffusion based model and the Monte Carlo based model for fuel and flibe temperature (and void) feedback effect. Error bar shows statistical error in Monte Carlo results.} 
  \label{fig:fuel_feedback}
\end{figure}

@@

\subsection{Steady state results}
After careful code-to-code verification for the multi-physics model, parameters such as power, flibe and fuel temperatures, and neutron flux are computed. Uniform temperature and uniform upward velocity are imposed as the inlet boundary condition. Vacuum boundary condition for neutron diffusion is used outside of the reflector.

% flux
\begin{figure}
  \centering
  \begin{subfigure}[b]{0.46\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{./images/diffusion/tmsr/SS/non_ms/fast_flux.png}
        \caption{Fast neutron flux ([5.00E-07, 1.40] MeV)}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.46\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{./images/diffusion/tmsr/SS/non_ms/thermal_flux.png}
        \caption{Thermal neutron flux ([0.00, 5.00E-07] MeV)}
    \end{subfigure}
    \caption{Steady state neutron flux}
    \label{fig:ss_res_flux}
\end{figure}

An eight-group energy structure is used in the neutron diffusion equations but the neutron flux values are regrouped into thermal ([0.00E+00, 5.00E-07] MeV) and fast ([5.00E-07, 1.40E+00] MeV) regions for plotting purpose. As confirmed by the plots, fast neutrons are generated exclusively from nuclear reactions in the fuel region and are then scattered by the matters in the core as they get thermalized. 
The moderation effect of the coolant is dwarfed by that of the graphite reflector in TMSR. As a result, a large portion of thermal neutrons is found inside the reflector, besides the center of the core.

The thermal neutrons that travel back from the reflector to the fuel region cause a peak in power density near the border as they trigger nuclear reactions.

% power
\begin{figure}

        \begin{subfigure}{0.45\textwidth}
        \centering
        \includegraphics[width=0.8\textwidth]{./images/diffusion/tmsr/SS/non_ms/Pdensity(steady_state).png}
        \end{subfigure}
        ~
        \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=0.8\textwidth]{./images/diffusion/tmsr/SS/non_ms/power_peaking_r.png}
        \includegraphics[width=0.8\textwidth]{./images/diffusion/tmsr/SS/non_ms/power_peaking_z.png}
        \caption*{Radial and axial power profile}
    \end{subfigure}%

    \caption{Power distribution in TMSR SF-1}
    \label{fig:tmsr_power_ss}
\end{figure}

As shown in figure \ref{fig:tmsr_power_ss}, the power peaks at the center of the fuel region, decreases outward and increases again next to the reflector boundaries due to the moderation effect of the graphite reflector. This confirms that the neutron diffusion based model captures the boundary effect adequately. The radial power peaking in TMSR SF-1 is 1.24 at nominal conditions with fresh fuel.

@@

The Fick's law assumption in diffusion models does not take directional variations in neutron transport into account, and this assumption is violated in strong absorbers such as control rods.
This section describes a control rods modeling method based on the $SP_3$ approximation of NTE that is more accurate than the diffusion approximation, especially in control rod regions, and yet is considerably less expensive than the discrete ordinates ($S_N$) or spherical harmonics ($P_N$) approaches. In addition, the $SP_3$ equations can be solved in the same manner as the diffusion equations, which allows similar implementations with the same tools.
